Temperature Measurements in Optical Tweezer Experiments

### 2017-01-02 doc/draft1.tex
updated draft

\subsection{Surrounding Gas - Barostat}
Without any equilibrating mechanism the setup described by now would lead to the system melting, which is not desirable. In the next step we will 
introduce the surrounding gas of the gas chamber that will absorb some of the energy in the system, leading to the final state.\\
Generally, pressure is introduced to the system by surrounding the object of interest (in this case the glass nano sphere) with a pressure medium.
There are two main requirements for the choice of such a pressure medium: the exerted pressure must be hydrostatic and the computation of the
interaction between the pressure medium and the object of interest must not take up a lot of resources.\\
The model used in this thesis was developed by Gr\"unwald and Dellago \cite{Gruenwald2006} and uses an ideal gas of non-interacting particles as
pressure medium. The particles of this pressure medium flow into the simulation from an outside box, whose geometry is based on the form of the object
of interest. This barostat also acts as a thermostat and thus is suitable for the application in this thesis.\\
The gas particles interact with the object via a soft-sphere potential of the form
\begin{equation}
    \label{eq:softsphere}
    U(r) = \frac{1}{r^{12}}
\end{equation}
in reduced units. \\
BLABLABLA\\
The algorithm can be performed by following these steps:
\begin{enumerate}
    \item Randomly draw the number of particles that are created on a single side of the minimal volume of cells, $N_\text{fac}$, from the
        distribution 
        \begin{equation}
            \langle N_\text{fac}\rangle = \Delta t L^2 P \left(\frac{1}{2\pi m k_B T}\right)^\frac12
        \end{equation}
        where $\Delta T$ is the time step of the simulation, $L$ is the side length of the cell in which the particle is created, $P$ is the desired
        pressure, $m$ is the mass of the gas particle, $k_B$ is the Boltzmann constant (which will be set to 1 in reduced units) and $T$ is the
        desired temperature. This chosen number of particles is then equally distributed over the face of the cell on which they are created.
    \item wos
\end{enumerate}

>>>>

\subsection{Surrounding Gas - Barostat}
Without any equilibrating mechanism the setup described by now would lead to the system melting, which is not desirable. In the next step we will 
introduce the surrounding gas of the gas chamber that will absorb some of the energy in the system, leading to the final state.\\
Generally, pressure is introduced to the system by surrounding the object of interest (in this case the glass nano sphere) with a pressure medium.
There are two main requirements for the choice of such a pressure medium: the exerted pressure must be hydrostatic and the computation of the
interaction between the pressure medium and the object of interest must not take up a lot of resources.\\
The model used in this thesis was developed by Gr\"unwald and Dellago \cite{Gruenwald2006} and uses an ideal gas of non-interacting particles as
pressure medium. The particles of this pressure medium flow into the simulation from an outside box, whose geometry is based on the form of the object
of interest. This barostat also acts as a thermostat and thus is suitable for the application in this thesis.\\
The gas particles interact with the object via a soft-sphere potential of the form
    \label{eq:softsphere}
    U(r) = \frac{1}{r^{12}}
in reduced units. \\
BLABLABLA\\
The algorithm can be performed by following these steps:
    \item Randomly draw the number of particles that are created on a single side of the minimal volume of cells, $N_\text{fac}$, from the
        distribution 
            %\langle N_\text{fac}\rangle = \Delta t L^2 P \left(\frac{1}{2\pi m k_B T}\right)^\frac12
            \langle N_\text{fac}\rangle = \Delta t L^2 P \sqrt{\frac{1}{2\pi m k_B T}}
        where $\Delta t$ is the time step of the simulation, $L$ is the side length of the cell in which the particle is created, $P$ is the desired
        pressure, $m$ is the mass of the gas particle, $k_B$ is the Boltzmann constant (which will be set to 1 in reduced units) and $T$ is the
        desired temperature. This chosen number of particles is then equally distributed over the face of the cell on which they are created. The
        velocities of the created particles are drawn from two different random number distributions. The component of the particle perpendicular to
        the surface is drawn from a Rayleigh distribution of the form 
            p(v_i) = \frac{m}{k_B T}v_i \ e^{-\frac{mv_i^2}{2k_BT}}
        The other components of the particles' velocity are drawn from a Maxwell-Boltzmann distribution.
    \item Perform the first step of the velocity Verlet algorithm to propagate the particle positions by one time step.
    \item Check if any gas particles have left the minimal volume of cells and remove those which have.
    \item Check if the geometry of the crystal and with it the minimal volume of cells has changed. If it has, remove all gas particles in the cells
        that are no longer needed. Then insert new gas particles to the created cells with a number drawn from a Poisson distribution with mean value
            \langle N_\text{ins}\rangle = \frac{PL^3}{k_BT}
        If the length of the cell $L$ is chosen to be equal to the cut-off radius $r_c$, this insertion should only be carried out with a probablity of
            P_\text{ins} = e^{-\frac{U}{k_BT}} < 1
        (where U is the interaction energy between the gas particle and the crystal) because it is possible that the inserted particle is 
        within the interaction range of the crystal. 
    \item Compute all forces.
    \item Perform the second step of the velocity Verlet and propagate the particle velocities by one time step. 
This algorithm is formulated in a general fashion, so that a wide range of crystals and geometries can be used. The setup used in this thesis is a
FCC lattice, which has a nice symmetry that is not influenced by the surrounding gas. The algorithm will therefore not be carried out using 
cell-lists and a minimal volume of cells that is changing over the course of the simulation, but rather a fixed setup of the volume surrounding the 
nano crystal.\\ 
Since the crystal itself is a cube a straighforward approach is surrounding it by a bigger cube.
